---
title: "Untitled"
author: "Cameron Bale"
date: "8/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install.packages(c('tidyverse', 'sp', 'patchwork', 'ggridges', 'spatstat', 'ggmap', 'geosphere'))
library(plyr)
library(tidyverse)
library(sp)
library(patchwork)
library(ggridges)
library(spatstat)
library(ggmap)
library(geosphere)
```

Read in data.
```{r}
load(file = "../Data/korea_data_clean.RData")
head(full)
```

How many individuals in the data?
```{r}
full %>%
  distinct(patient_id) %>%
  summarize(n = n())
```

What time frame does the data cover?
```{r}
full %>%
  summarize(min_date = min(date),
            max_date = max(date))
```

What are the minimum and maximum trajectory lengths?
```{r}
full %>%
  group_by(patient_id) %>%
  summarize(n = n(), .groups = 'drop') %>%
  summarize(min_length = min(n),
            max_length = max(n))
```

How many location points do individuals typically have?
```{r}
full %>%
  group_by(patient_id) %>%
  summarize(n = n(), .groups = 'keep') %>%
  ggplot(aes(x = n)) +
  geom_histogram(binwidth = 1) +
  labs(title = 'Trajectory Length Distribution',
       y = 'Count',
       x = 'Trajectory Length')
```

How many unique location points are there, and what is the percentage of unique location points?
```{r}
(np <- full %>%
  distinct(latitude, longitude) %>%
  summarize(n = n(), .groups = 'drop') %>%
  pull())

nup <- full %>%
  group_by(latitude, longitude) %>%
  summarize(n = n(), .groups = 'drop') %>%
  filter(n == 1) %>%
  summarize(n = n()) %>%
  pull()

nup/np * 100
```

What percentage of individuals have a unique location trajectory?
```{r}
split_trajs <- full %>%
  select(patient_id, latitude, longitude) %>%
  group_by(patient_id) %>%
  arrange(latitude) %>%
  group_split(.keep = FALSE)

length(unique(split_trajs))/length(split_trajs) * 100
```

Calculate the density of points per square kilometer in the full dataset, excluding 16 points on an island South of the mainland (below 34 degrees latitude).
```{r}
# original data is in latitude and longitude
# have to project it onto a 2D space in terms of meters and divide by 1000 to get it in kilometers
# https://proj.org/operations/projections/utm.html
# it is a universal transverse mercator projection using the sp package
f <- full %>%
  select(longitude, latitude) %>%
  filter(latitude > 34)

coordinates(f) <- c("longitude", "latitude")
proj4string(f) <- CRS("+proj=longlat +datum=WGS84")
fm <- spTransform(f, CRS("+proj=utm +zone=52"))
fm <- as.data.frame(fm)/1000

# define window to calculate intensity in by the bounds created by the minimum and maximum observed latitude and longitude values
window <- data.frame(
  min_long = min(fm$longitude),
  min_lat = min(fm$latitude),
  max_long = max(fm$longitude),
  max_lat = max(fm$latitude)
)

# create ppp object to pass to intensity function
f_ppp <- ppp(fm$longitude, fm$latitude, c(window$min_long, window$max_long), c(window$min_lat, window$max_lat))

intensity(f_ppp)
```

Calculate the density of points per square kilometer in Seoul.
```{r}
s <- full %>%
  filter((longitude > 126.85 & longitude < 127.15) & (latitude > 37.45 & latitude < 37.65)) %>%
  select(longitude, latitude)

coordinates(s) <- c("longitude", "latitude")
proj4string(s) <- CRS("+proj=longlat +datum=WGS84")
sm <- spTransform(s, CRS("+proj=utm +zone=52"))
sm <- as.data.frame(sm)/1000

s_window <- data.frame(
  min_long = min(sm$longitude),
  min_lat = min(sm$latitude),
  max_long = max(sm$longitude),
  max_lat = max(sm$latitude)
)

s_ppp <- ppp(sm$longitude, sm$latitude, c(s_window$min_long, s_window$max_long), c(s_window$min_lat, s_window$max_lat))

intensity(s_ppp)
```

Output maps of the full dataset and Seoul.
```{r fig.width = 10, fig.height = 8}
k_map <- ggmap(get_map(location = c(126, 33, 130, 38.5)), 
               extent = 'panel', 
               base_layer = ggplot(full, aes(x = longitude, y = latitude))) +
  geom_point(alpha = 0.4, color = 'blue') +
  labs(x = 'Longitude',
       y = 'Latitude')

print(k_map)
```

```{r}
s_map <- ggmap(get_map(location = c(126.85, 37.45, 127.15, 37.65)), 
               extent = 'panel', 
               base_layer = ggplot(full, aes(x = longitude, y = latitude))) +
  geom_point(alpha = 0.4, color = 'blue') +
  labs(x = 'Longitude',
       y = 'Latitude')

print(s_map)
```

Calculating distance between points for individual i (From paper).
```{r}
distGeo(c(127.0170, 37.59256), c(127.017, 37.593))
```

Load uniqueness calculations from `korean_trajectories_analysis.Rmd`. Create side-by-side plot of uniqueness results for all of South Korea and Seoul.
```{r fig.width = 10, fig.height = 8}
# load percent unique data from all South Korea
load('../Data/pct_unique_5d.RData')
load('../Data/pct_unique_4d.RData')
load('../Data/pct_unique_3d.RData')
load('../Data/pct_unique_2d.RData')
load('../Data/pct_unique_1d.RData')
load('../Data/pct_unique_0d.RData')

# load percent unique data from Seoul
load('../Data/s_pu_5d.Rdata')
load('../Data/s_pu_4d.Rdata')
load('../Data/s_pu_3d.Rdata')
load('../Data/s_pu_2d.Rdata')
load('../Data/s_pu_1d.Rdata')
load('../Data/s_pu_0d.Rdata')

full_pd <- up_5d %>%
  bind_rows(up_4d, up_3d, up_2d, up_1d, up_0d)

full_s <- sup_5d %>%
  bind_rows(sup_4d, sup_3d, sup_2d, sup_1d, sup_0d)

boxes_full <- full_pd %>%
  mutate(specificity = factor(specificity, levels = c('0', '1', '2', '3', '4', '5')),
         num_points = factor(num_points, levels = c('one', 'two', 'three', 'four', 'five'))) %>%
  ggplot(aes(x = specificity, y = percent_unique, fill = factor(num_points))) +
  geom_boxplot(position = position_dodge(width = 0)) +
  labs(x = '',
       y = '% Unique Trajectories',
       fill = '# Lat/Long Points\n') +
  scale_fill_discrete(labels = c('One', 'Two', 'Three', 'Four', 'Five'),
                      guide = guide_legend(reverse = TRUE)) +
  theme(legend.position = c(.9, .25),
        legend.justification = c('right', 'bottom'),
        legend.box.just = 'right')

boxes_s <- full_s %>%
  mutate(specificity = factor(specificity, levels = c('0', '1', '2', '3', '4', '5')),
         num_points = factor(num_points, levels = c('one', 'two', 'three', 'four', 'five'))) %>%
  ggplot(aes(x = specificity, y = percent_unique, fill = factor(num_points))) +
  geom_boxplot(position = position_dodge(width = 0)) +
  labs(x = '',
       y = '',
       fill = '# Lat/Long Points\n') +
  scale_fill_discrete(labels = c('One', 'Two', 'Three', 'Four', 'Five'),
                      guide = guide_legend(reverse = TRUE)) +
  theme(legend.position = c(.9, .25),
        legend.justification = c('right', 'bottom'),
        legend.box.just = 'right',
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

boxes_full | boxes_s
```

Create map showing coarsened trajectories.
```{r fig.width = 10, fig.height = 8}
trajectories <- full %>%
  select(patient_id, latitude, longitude) %>%
  group_by(patient_id) %>%
  filter(n() > 4) %>%
  drop_na() %>%
  ungroup()

traj_1d <- trajectories %>%
  mutate(latitude2 = round(latitude, digits = 1),
         longitude2 = round(longitude, digits = 1),
         latitude = latitude2,
         longitude = longitude2) %>%
  select(-latitude2, -longitude2)

coarse_k_map <- ggmap(get_map(location = c(126, 33, 130, 38.5)), 
               extent = 'panel', 
               base_layer = ggplot(traj_1d, aes(x = longitude, y = latitude))) +
  geom_point(alpha = 0.4, color = 'blue') +
  labs(x = 'Longitude',
       y = 'Latitude')

print(coarse_k_map)
```

```{r}
coarse_s_map <- ggmap(get_map(location = c(126.85, 37.45, 127.15, 37.65)), 
               extent = 'panel', 
               base_layer = ggplot(traj_1d, aes(x = longitude, y = latitude))) +
  geom_point(color = 'blue') +
  labs(x = 'Longitude',
       y = 'Latitude')

print(coarse_s_map)
```

Calculate percentage and number of coarsened location points meeting the requirement of no singling-out (for counts section of paper). Using full data.
```{r}
bin_dist <- function(loc_data, num_dec_lat, num_dec_long) {
  
  loc_data %>%
    group_by(patient_id) %>%
    filter(n() > 4) %>%
    transmute(latitude = round(latitude, num_dec_lat),
              longitude = round(longitude, num_dec_long)) %>%
    group_by(latitude, longitude) %>%
    summarize(n = n(), .groups = 'drop') %>%
    select(n) %>%
    mutate(d = factor(num_dec_lat))
  
}

bin_dists <- bin_dist(full, num_dec_lat = 5, num_dec_long = 4) %>%
  bind_rows(bin_dist(full, num_dec_lat = 4, num_dec_long = 4),
            bin_dist(full, num_dec_lat = 3, num_dec_long = 3),
            bin_dist(full, num_dec_lat = 2, num_dec_long = 2),
            bin_dist(full, num_dec_lat = 1, num_dec_long = 1),
            bin_dist(full, num_dec_lat = 0, num_dec_long = 0))

bin_dists %>%
  ggplot(aes(x = n, y = d)) +
  geom_density_ridges(scale = 0.95, rel_min_height = 0.001) +
  xlim(0, 100)

p5 <- bin_dists %>%
  filter(d == 5) %>%
  ggplot(aes(x = n)) +
  geom_histogram(bins = 20) +
  xlim(0, 50)

p4 <- bin_dists %>%
  filter(d == 4) %>%
  ggplot(aes(x = n)) +
  geom_histogram(bins = 20) +
  xlim(0, 50)

p3 <- bin_dists %>%
  filter(d == 3) %>%
  ggplot(aes(x = n)) +
  geom_histogram(bins = 20) +
  xlim(0, 50)

p2 <- bin_dists %>%
  filter(d == 2) %>%
  ggplot(aes(x = n)) +
  geom_histogram(bins = 20) +
  xlim(0, 50)

p1 <- bin_dists %>%
  filter(d == 1) %>%
  ggplot(aes(x = n)) +
  geom_histogram(bins = 20) +
  xlim(0, 50)

p0 <- bin_dists %>%
  filter(d == 0) %>%
  ggplot(aes(x = n)) +
  geom_histogram(bins = 500) +
  xlim(0, 50)
```

```{r fig.width = 3, fig.height = 8}
p5/p4/p3/p2/p1/p0
```

What percent and number of locations are not in violation of singling-out?
```{r}
bin_dists %>%
  mutate(not_singled_out = if_else(n > 1, 1, 0)) %>%
  group_by(d) %>%
  summarize(pct_nso = mean(not_singled_out) * 100,
            num_nso = sum(not_singled_out), .groups = 'drop')
```

Calculate percent and number of locations not violating Singling-out for just Seoul.
```{r}
seoul_locs <- full %>%
  filter(province == 'Seoul')

bin_dists_s <- bin_dist(seoul_locs, num_dec_lat = 5, num_dec_long = 4) %>%
  bind_rows(bin_dist(seoul_locs, num_dec_lat = 4, num_dec_long = 4),
            bin_dist(seoul_locs, num_dec_lat = 3, num_dec_long = 3),
            bin_dist(seoul_locs, num_dec_lat = 2, num_dec_long = 2),
            bin_dist(seoul_locs, num_dec_lat = 1, num_dec_long = 1),
            bin_dist(seoul_locs, num_dec_lat = 0, num_dec_long = 0))

bin_dists_s %>%
  mutate(not_singled_out = if_else(n > 1, 1, 0)) %>%
  group_by(d) %>%
  summarize(pct_nso = mean(not_singled_out) * 100,
            num_nso = sum(not_singled_out), .groups = 'drop')
```

Add small random noise to latitude and longitude values. This should create the case where an external record cannot be matched to any record in the database.
```{r}
n_full <- full %>%
  mutate(latitude = latitude + runif(nrow(full), min = -0.5, 0.5),
         longitude = longitude + runif(nrow(full), min = -0.5, 0.5)) %>%
  select(patient_id, latitude, longitude)

n_full %>%
  distinct(latitude, longitude) %>%
  summarize(percent_unique = n()/nrow(n_full))

n_full_split <- n_full %>%
  group_by(patient_id) %>%
  filter(n() > 4) %>%
  group_split(.keep = FALSE)

ci <- lapply(n_full_split, sample_n, 1)

temp <- sapply(ci, function(x) sapply(n_full_split, function(y) match_df(y, x)))
```

Testing method for compatibility matrix.
```{r}
C <- sapply(n_full_split, function(x) sapply(n_full_split, function(y) identical(x, y)))

all(C[lower.tri(C)] == 0, C[upper.tri(C)] == 0)
```

Compatibility for original granularity for CI trajectory lengths of one to five points.
```{r}
o_full <- full  %>%
  select(patient_id, latitude, longitude) %>%
  group_by(patient_id) %>%
  filter(n() > 4) %>%
  group_split(.keep = FALSE)

C <- sapply(n_full_split, function(x) sapply(o_full, function(y) identical(x, y)))

sum(rowSums(C))
```

Trajectory uniqueness calculations for noisy trajectories.
```{r}
n_full <- n_full %>%
  group_by(patient_id) %>%
  filter(n() > 4) %>%
  ungroup()

pvar_names <- c('one', 'two', 'three', 'four', 'five')

nup_5d <- map_dfc(1:5, function(x) trajectory_uniqueness(data.table(n_full), num_points = x, nits = 100))

colnames(nup_5d) <- pvar_names

nup_5d <- nup_5d %>%
  gather(key = 'num_points', value = 'percent_unique') %>%
  mutate(specificity = 5)

save(nup_5d, file = '../Data/n_pu_5d.Rdata')

n_trajs_4d <- n_full %>%
  mutate(latitude2 = round(latitude, digits = 4),
         distances = distGeo(tibble(longitude, latitude), tibble(longitude, latitude2)),
         latitude = latitude2) %>%
  select(-latitude2)

nup_4d <- map_dfc(1:5, function(x) trajectory_uniqueness(data.table(n_trajs_4d[,c(1, 2, 3)]), num_points = x, nits = 100))

colnames(nup_4d) <- pvar_names

nup_4d <- nup_4d %>%
  gather(key = 'num_points', value = 'percent_unique') %>%
  mutate(specificity = 4)

save(nup_4d, file = '../Data/n_pu_4d.Rdata')

n_trajs_3d <- n_full %>%
  mutate(latitude2 = round(latitude, digits = 3),
         longitude2 = round(longitude, digits = 3),
         distances = distGeo(tibble(longitude, latitude), tibble(longitude2, latitude2)),
         latitude = latitude2,
         longitude = longitude2) %>%
  select(-latitude2, -longitude2)

nup_3d <- map_dfc(1:5, function(x) trajectory_uniqueness(data.table(n_trajs_3d[,c(1, 2, 3)]), num_points = x, nits = 100))

colnames(nup_3d) <- pvar_names

nup_3d <- nup_3d %>%
  gather(key = 'num_points', value = 'percent_unique') %>%
  mutate(specificity = 3)

save(nup_3d, file = '../Data/n_pu_3d.Rdata')

n_trajs_2d <- n_full %>%
  mutate(latitude2 = round(latitude, digits = 2),
         longitude2 = round(longitude, digits = 2),
         distances = distGeo(tibble(longitude, latitude), tibble(longitude2, latitude2)),
         latitude = latitude2,
         longitude = longitude2) %>%
  select(-latitude2, -longitude2)

nup_2d <- map_dfc(1:5, function(x) trajectory_uniqueness(data.table(n_trajs_2d[,c(1, 2, 3)]), num_points = x, nits = 100))

colnames(nup_2d) <- pvar_names

nup_2d <- nup_2d %>%
  gather(key = 'num_points', value = 'percent_unique') %>%
  mutate(specificity = 2)

save(nup_2d, file = '../Data/n_pu_2d.Rdata')

n_trajs_1d <- n_full %>%
  mutate(latitude2 = round(latitude, digits = 1),
         longitude2 = round(longitude, digits = 1),
         distances = distGeo(tibble(longitude, latitude), tibble(longitude2, latitude2)),
         latitude = latitude2,
         longitude = longitude2) %>%
  select(-latitude2, -longitude2)

nup_1d <- map_dfc(1:5, function(x) trajectory_uniqueness(data.table(n_trajs_1d[,c(1, 2, 3)]), num_points = x, nits = 100))

colnames(nup_1d) <- pvar_names

nup_1d <- nup_1d %>%
  gather(key = 'num_points', value = 'percent_unique') %>%
  mutate(specificity = 1)

save(nup_1d, file = '../Data/n_pu_1d.Rdata')

n_trajs_0d <- n_full %>%
  mutate(latitude2 = round(latitude, digits = 0),
         longitude2 = round(longitude, digits = 0),
         distances = distGeo(tibble(longitude, latitude), tibble(longitude2, latitude2)),
         latitude = latitude2,
         longitude = longitude2) %>%
  select(-latitude2, -longitude2)

nup_0d <- map_dfc(1:5, function(x) trajectory_uniqueness(data.table(n_trajs_0d[,c(1, 2, 3)]), num_points = x, nits = 100))

colnames(nup_0d) <- pvar_names

nup_0d <- nup_0d %>%
  gather(key = 'num_points', value = 'percent_unique') %>%
  mutate(specificity = 0)

save(nup_0d, file = '../Data/n_pu_0d.Rdata')
```

Figure showing uniqueness calculations for noisy trajectories.
```{r fig.width = 10, fig.height = 8}
noisy_full <- nup_5d %>%
  bind_rows(nup_4d, nup_3d, nup_2d, nup_1d, nup_0d)

noisy_boxes <- noisy_full %>%
  mutate(specificity = factor(specificity, levels = c('0', '1', '2', '3', '4', '5')),
         num_points = factor(num_points, levels = c('one', 'two', 'three', 'four', 'five'))) %>%
  ggplot(aes(x = specificity, y = percent_unique, fill = factor(num_points))) +
  geom_boxplot(position = position_dodge(width = 0)) +
  labs(x = '',
       y = '% Unique Trajectories',
       fill = '# Lat/Long Points\n') +
  scale_fill_discrete(labels = c('One', 'Two', 'Three', 'Four', 'Five'),
                      guide = guide_legend(reverse = TRUE)) +
  theme(legend.position = c(.9, .25),
        legend.justification = c('right', 'bottom'),
        legend.box.just = 'right')

noisy_boxes
```

```{r}
full %>%
    group_by(patient_id) %>%
    filter(n() > 4) %>%
    transmute(latitude = round(latitude, num_dec_lat),
              longitude = round(longitude, num_dec_long)) %>%
    group_by(latitude, longitude) %>%
    summarize(n = n(), .groups = 'drop') %>%
    select(n) %>%
    mutate(d = factor(num_dec_lat))
```


```{r fig.height=7, fig.width= 9}
traj_long <- full %>%
  select(patient_id, latitude, longitude) %>%
  group_by(patient_id) %>%
  filter(n() > 4)

match_calc <- function(location_data, sample_size) {
  
  split_data <- location_data %>%
    sample_n(sample_size) %>%
    arrange(patient_id, latitude) %>%
    group_split(.keep = FALSE)
  
  match_data <- tibble(which_match = match(split_data, unique(split_data))) %>%
    group_by(which_match) %>%
    mutate(n = 1/n()) %>%
    pull(n)
  
  return(match_data)

}

inf_calc <- function(location_data, num_dec, nits = 100, sample_sizes = 1:5, pvar_names = c('one', 'two', 'three', 'four', 'five')) {
  
  location_data <- location_data %>%
    mutate_at(.vars = c('latitude', 'longitude'), round, digits = num_dec)
  
  props <- map_dfc(sample_sizes, function(x) rowMeans(map_dfc(1:nits, function(y) match_calc(location_data, x))))
  
  colnames(props) <- pvar_names
  
  props <- props %>%
    gather(key = 'num_points', value = 'inf_prop') %>%
    mutate(specificity = num_dec)
  
  return(props)
  
}

inf_results <- inf_calc(traj_long, 5) %>%
  bind_rows(inf_calc(traj_long, 4)) %>%
  bind_rows(inf_calc(traj_long, 3)) %>%
  bind_rows(inf_calc(traj_long, 2)) %>%
  bind_rows(inf_calc(traj_long, 1)) %>%
  bind_rows(inf_calc(traj_long, 0))

i_p <- inf_results %>%
  mutate(specificity = factor(specificity, levels = c('0', '1', '2', '3', '4', '5')),
         num_points = factor(num_points, levels = c('one', 'two', 'three', 'four', 'five'))) %>%
  ggplot(aes(x = specificity, y = inf_prop, fill = factor(num_points))) +
  geom_boxplot() +
  labs(x = 'Number of decimals d',
       y = TeX("$\\textbf{i}_{\\hat{\\textbf{y}}}$"),
       fill = 'CI Length\n') +
  scale_fill_discrete(labels = c('One', 'Two', 'Three', 'Four', 'Five'),
                      guide = guide_legend(reverse = TRUE)) +
  theme(legend.position = c(.99, 0.01),
        legend.justification = c('right', 'bottom'),
        legend.box.just = 'right') +
  ggtitle('Distribution of i Over Varying CI Lengths 1-5 and d = 1-5')

addSmallLegend <- function(myPlot, pointSize = 2, textSize = 10, spaceLegend = 1) {
    myPlot +
        guides(shape = guide_legend(override.aes = list(size = pointSize)),
               color = guide_legend(override.aes = list(size = pointSize))) +
        theme(legend.title = element_text(size = textSize), 
              legend.text  = element_text(size = textSize),
              legend.key.size = unit(spaceLegend, "lines"))
}

addSmallLegend(i_p)
```


```{r}
count_prop <- function(location_data, num_dec) {
  
  location_data <- location_data %>%
    mutate_at(.vars = c('latitude', 'longitude'), round, digits = num_dec)
  
  inf_props <- location_data %>%
    group_by(latitude, longitude) %>%
    mutate(inf_prop = 1/n()) %>%
    ungroup() %>%
    select(inf_prop)
  
  return(inf_props)
  
}

count_inf <- map_dfc(0:5, function(x) count_prop(traj_long, x))

colnames(count_inf) <- c('zero', 'one', 'two', 'three', 'four', 'five')

count_inf <- count_inf %>%
  gather(key = 'd', value = 'inf_prop')

count_inf %>%
  ggplot(aes(x = inf_prop, y = factor(d, levels = c('zero', 'one', 'two', 'three', 'four', 'five')))) +
  geom_boxplot() +
  labs(x = 'Individual Inference',
       y = 'Number of Digits after the Decimal')
```


### Assessing Inference

Create data objects for full korea and seoul.
```{r}
load(file = "../Data/korea_data_clean.RData")

full <- full %>%
  group_by(patient_id) %>%
  filter(n() > 4) %>%
  ungroup()
  
s_full <- full %>%
  filter(province == 'Seoul') %>%
  group_by(patient_id) %>%
  filter(n() > 4) %>%
  ungroup()

full <- full %>%
  select(patient_id, latitude, longitude)

s_full <- s_full %>%
  select(patient_id, latitude, longitude)
```

```{r}
ci_length = 3

status_data <- location_data %>% 
  group_by(patient_id) %>%
  mutate(status = sample(c(0, 1), size = 1, prob = c(.99, .01))) %>%
  ungroup()

ptv_inds <- status_data %>%
  filter(status == 1)

ci <- ptv_inds %>%
  group_by(patient_id) %>%
  sample_n(size = ci_length) %>%
  group_split()

ci <- lapply(ci, function(x) x %>% select(-patient_id, -status))

ci <- lapply(ci, function(x) x %>% group_by(latitude, longitude) %>% summarize(n = n(), .groups = 'drop'))

matches <- lapply(ci, function(y) match_df(status_data, y, on = c('latitude', 'longitude')) %>%
                                  group_by(patient_id, latitude, longitude, status) %>%
                                  summarize(n1 = n(), .groups = 'drop'))

links <- lapply(1:length(ci), function(x) left_join(matches[[x]], ci[[x]], by = c('latitude', 'longitude')))

links <- lapply(1:length(ci), function(x) links[[x]] %>% group_by(patient_id) %>% filter(n1 >= n & n() >= nrow(ci[[x]])) %>% ungroup())

covid_count <- lapply(links, function(x) distinct(x, patient_id, status))

inf_props <- map_dfr(covid_count, function(x) x %>% summarize(cond = mean(status) - prior))

(avg_cond <- inf_props %>% summarize(avg_cond = mean(cond)))
```

Create inference simulation function to simulate a small number of people with COVID. Explicitly require that there be at least one individual with COVID or else re-sample.
```{r}
inference_simulation <- function(loc_data, ci_length, prior = 0.01) {

  pos <- 0
  
  while(pos == 0) {
    
    status_data <- loc_data %>% 
      group_by(patient_id) %>%
      mutate(status = sample(c(0, 1), size = 1, prob = c(.99, .01))) %>%
      ungroup()
    
    ptv_inds <- status_data %>%
      filter(status == 1)
    
    pos <- nrow(ptv_inds)
    
  }
  
  ci <- ptv_inds %>%
    group_by(patient_id) %>%
    sample_n(size = ci_length) %>%
    group_split()

  ci1 <- lapply(ci, function(x) x %>% select(-patient_id, -status))

  ci2 <- lapply(ci1, function(x) x %>% group_by(latitude, longitude) %>% summarize(n = n(), .groups = 'drop'))
  
  matches <- lapply(ci2, function(y) match_df(status_data, y, on = c('latitude', 'longitude')) %>%
                                     group_by(patient_id, latitude, longitude, status) %>%
                                     summarize(n1 = n(), .groups = 'drop'))
  
  links <- lapply(1:length(ci2), function(x) left_join(matches[[x]], ci2[[x]], by = c('latitude', 'longitude')))

  links2 <- lapply(1:length(links), function(x) links[[x]] %>% group_by(patient_id) %>% filter(n1 >= n & n() >= nrow(ci2[[x]])) %>% ungroup())

  covid_count <- lapply(links2, function(x) distinct(x, patient_id, status))

  inf_props <- map_dfr(covid_count, function(x) x %>% summarize(cond = mean(status) - prior))

  avg_cond <- inf_props %>% summarize(avg_cond = mean(cond))
  
  return(avg_cond)
  
}
```

```{r}
inference_simulation(s_full, 3)
```

```{r}
inf_calc <- function(location_data, num_dec, nits = 100, sample_sizes = 1:5, pvar_names = c('one', 'two', 'three', 'four', 'five')) {
  
  loc_data <- location_data %>%
    mutate_at(.vars = c('latitude', 'longitude'), round, digits = num_dec)
  
  props <- map_dfc(1:5, function(y) map_dfr(1:100, function(x) inference_simulation(loc_data, y)))
  
  colnames(props) <- pvar_names
  
  props_g <- props %>%
    gather(key = 'num_points', value = 'inf_prop') %>%
    mutate(specificity = num_dec)
  
  return(props_g)
  
}
```

```{r fig.width = 9, fig.height=6}
inf_results <- inf_calc(full, 5) %>%
  bind_rows(inf_calc(full, 4)) %>%
  bind_rows(inf_calc(full, 3)) %>%
  bind_rows(inf_calc(full, 2)) %>%
  bind_rows(inf_calc(full, 1)) %>%
  bind_rows(inf_calc(full, 0))

i_p <- inf_results %>%
  mutate(specificity = factor(specificity, levels = c('0', '1', '2', '3', '4', '5')),
         num_points = factor(num_points, levels = c('one', 'two', 'three', 'four', 'five'))) %>%
  ggplot(aes(x = specificity, y = inf_prop, fill = factor(num_points))) +
  geom_boxplot() +
  labs(x = 'Number of decimals d',
       y = 'Change in Probability of Inference',
       fill = 'CI Length\n') +
  scale_fill_discrete(labels = c('One', 'Two', 'Three', 'Four', 'Five'),
                      guide = guide_legend(reverse = TRUE)) +
  theme(legend.position = c(.99, 0.01),
        legend.justification = c('right', 'bottom'),
        legend.box.just = 'right') +
  ggtitle('Distribution of i Over Varying CI Lengths 1-5 and d = 1-5')

addSmallLegend <- function(myPlot, pointSize = 2, textSize = 10, spaceLegend = 1) {
    myPlot +
        guides(shape = guide_legend(override.aes = list(size = pointSize)),
               color = guide_legend(override.aes = list(size = pointSize))) +
        theme(legend.title = element_text(size = textSize), 
              legend.text  = element_text(size = textSize),
              legend.key.size = unit(spaceLegend, "lines"))
}

addSmallLegend(i_p)
```

### Inference Analysis for Counts

Full south Korea data.
```{r}
inf_counts <- function(location_data, num_dec, prior = 0.01) {
  
  num_pos <- 0
  
  while(num_pos == 0) {
    
    status_data <- location_data %>% 
      group_by(patient_id) %>%
      mutate(status = sample(c(0, 1), size = 1, prob = c(.99, .01))) %>%
      ungroup()
    
    ptv_inds <- status_data %>%
      filter(status == 1)
    
    num_pos <- nrow(ptv_inds)
    
  }
  
  c_status_data <- status_data %>%
    mutate_at(.vars = c('latitude', 'longitude'), round, digits = num_dec)
  
  covid_locs <- c_status_data %>%
    filter(status == 1) %>%
    distinct(latitude, longitude)
  
  count_props <- match_df(c_status_data, covid_locs, on = c('latitude', 'longitude')) %>%
    group_by(latitude, longitude) %>%
    summarize(inc_inf = mean(status) - prior, .groups = 'drop') %>%
    summarize(avg_inc_inf = mean(inc_inf)) %>%
    mutate(specificity = num_dec)
    
  return(count_props)
    
}

inf_count_dists <- map_dfr(0:5, function(y) map_dfr(1:100, function(x) inf_counts(full, y))) %>%
  mutate(specificity = factor(specificity, levels = c('0', '1', '2', '3', '4', '5')))

count_inf_full <- inf_count_dists %>%
  ggplot(aes(x = specificity, y = avg_inc_inf)) +
  geom_boxplot() +
  labs(x = 'Number of decimals d',
       y = 'Average Change in Probability of Inference') +
  scale_y_continuous(limits = c(-.05, 1), breaks = seq(0, 1.1, by = .25))
```

```{r}
inf_count_dists_s <- map_dfr(0:5, function(y) map_dfr(1:100, function(x) inf_counts(s_full, y))) %>%
  mutate(specificity = factor(specificity, levels = c('0', '1', '2', '3', '4', '5')))

count_inf_s <- inf_count_dists_s %>%
  ggplot(aes(x = specificity, y = avg_inc_inf)) +
  geom_boxplot() +
  labs(y = '',
       x = 'Number of decimals d') +
  scale_y_continuous(limits = c(-.05, 1), breaks = seq(0, 1.1, by = .25))
```

```{r}
count_inf_full | count_inf_s 
```





















